CommonMind Consortium: DLPFC

### 2020-09-17 combined_analysis/diff.networks.Rmd
Update diff networks

## Difference networks
```{r diff.networks}

@@

```{r modules.in.second.cohort, fig.width=8, fig.height=40}

>>>>

# Sex network
## Difference networks
```{r diff.networks}

@@

```{r modules.in.second.cohort, fig.width=8, fig.height=100}

# Disease network
## Difference networks
```{r diff.networks.Dx}

resVersion = "Dx"
variable = 'Dx'

```{r testing.Dx}

```{r plot.discovery.Dx}
# plot discovery and testing
ggplot(df_test, aes(Module, -log10(FDR))) + geom_bar(stat='identity', fill=df_test$Module) + theme_bw() + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black")) + coord_flip() + facet_wrap(~Cohort) + ylab(bquote(-log[10]~FDR)) + scale_y_continuous(expand=c(0,0)) + geom_hline(yintercept = -log10(0.05), color="red", linetype="dashed")
```

```{r modules.in.discovery.Dx, fig.width=10, fig.height=20}

```{r second.cohort.Dx, fig.width=6, fig.height=12}
df_cohort2 = df_test[df_test$Cohort == "NIMH-HBCC",]
df_cohort2$Module = factor(df_cohort2$Module, unique(df_cohort2$Module))
table(df_cohort2$FDR < 0.05)

```{r modules.in.second.cohort.Dx, fig.width=8, fig.height=40}
